\subsection{Lepton Flavour Violation}

The violation of lepton number (LNV) and lepton flavour conservation (LFV) are strictly prohibited
inside the SM, with the notable exception of neutrino oscillations, producing negligibly 
small effects in the charged sector. 
The discovery of a LNV or LFV decay of a known particle would be therefore a striking evidence 
of physics beyond the SM. 

A reach program of searches for LNV and LFV decays is undergoing at the LHC experiments. 
While the LHCb experiment can cover the full spectrum of beauty, charm and $\tau$ decays, 
the ATLAS and CMS experiments, given the low $p_T$ involved do concentrate on specific decays which are easier to trigger. 

LHCb has set world best upper limits on $B^0_{(s)} \to e \mu$~\cite{Aaij:2013cby} 
and $D^0 \to e \mu$~\cite{Aaij:2015qmj} decays and has set a competitive
limit on $\tau \to \mu\mu\mu$ decays, contributing to improve the world combined limit \cite{Aaij:2014azz}. 
Also the ATLAS experiment has contributed recently on the same decay by looking for $\tau \to \mu\mu\mu$
where the $\tau$ comes from a $W$ boson leptonic decay~\cite{Aad:2016wce}; the sensitivity of this search is not yet 
competitive with LHCb and B-factories but proves the feasibility of suche a delicate analysis in the high $p_T$ 
environment. 
Finally among the searches for LNV the most prominent is the LHCb search for prompt or long-living Majorana neutrinos 
in $B^+\to \pi^- \mu^+ \mu^+$ decays~\cite{Aaij:2012zr}.

Already exploiting Run I data many other searches are in progress in the whole family of $B\to X e\	mu$ decays and 
$B\to X \mu\tau$ decays where $X$ is a SM hadron. 

All the mentioned searches will be continued with Run II data aiming for new physics or pushing further the limits on 
LFV and LNV couplings. 
During these period the Belle II experiment will start accumulating data and will compete strongly on the same channels. 
While channels with muons, being easy to trigger, are essentially limited by the collected luminosity, the others will
profit of the improved LHCb trigger in Run II and will stay as key measurement also for the Upgrade. 


