% Please use the skeleton file you have received in the
% invitation-to-submit email, where your data are already
% filled in. Otherwise please make sure you insert your
% data according to the instructions in PoSauthmanual.pdf
\documentclass{PoS}

\newcommand{\theInvRho}{\frac{\varepsilon_{\mu^+\mu^-}}{\varepsilon_{J/\psi K^{\pm}}}}
\newcommand{\pt}{$p_{\rm{T}}$}
\newcommand{\gev}{\rm{GeV}}

\title{Beauty and charm rare decays}

\ShortTitle{Beauty and charm rare decays}

\author{\speaker{U. De Sanctis, F.Dettori, S. Fiorendi}\thanks{A footnote may follow.}\\
        Author affiliation\\
        E-mail: \email{author@email}}

%\author{Another Author\\
%        Affiliation\\
%        E-mail: \email{...}}

\abstract{..........................\
          ...........................}

\FullConference{VII Workshop italiano sulla fisica pp a LHC\\
		16-18 Maggio 2016\\
		Pisa, Italy}


\begin{document}

%\section{...}
\include{intro}
\include{ppLHC_desanctis}

\clearpage



\begin{thebibliography}{99}
\bibitem{CMS} CMS Collaboration, 
{\it{CMS, the Compact Muon Solenoid: technical proposal}},
LHC Tech. Proposal (1994) 
https://cds.cern.ch/record/290969

\bibitem{ATLAS} Armstrong, W. W. and others, 
{\it{ATLAS: Technical proposal for a general-purpose p p experiment at the Large Hadron Collider at CERN}},
CERN-LHCC-94-43 

\bibitem{LHCb} LHCb Collaboration, 
{\it{LHCb : Technical Proposal}},
Tech. Proposal (1998) https://cds.cern.ch/record/622031

\bibitem{Bobeth} Bobeth C. et al., {\it{$B_{s,d} \to l^+ l^-$ in the Standard Model with Reduced Theoretical Uncertainty}}, Phys. Rev. Lett., {\bf{112}}, 101801, 2014.
\bibitem{Nature} CMS and LHCb Collaborations, {\it{Observation of the rare $B^0_s\rightarrow\mu^+\mu^-$ decay from the combined analysis of CMS and LHCb data}}, Nature, {\bf{522}}, 2015.
\bibitem{ATLAS} ATLAS Collaboration, {\it{Study of the rare decays of $B^0_s$ and $B^0$  into muon pairs from data collected during the LHC Run 1 with the ATLAS detector}}, arXiv:1604.04263 [hep-ex], 2016. {\it{Submitted to Eur.Phys. J. C}}.
\bibitem{mumuK_LHCb} LHCb Collaboration, {\it{Angular analysis of the $B^0 \to K^{*0}  \mu^+ \mu^-$ decay using 3~${\rm{fb^{-1}}}$ of integrated luminosity}}, JHEP {\bf{02}} 104, 2016. 
\bibitem{mumuK_CMS} CMS Collaboration, {\it{Angular analysis of the $B^0 \to K^{*0}  \mu^+ \mu^-$  decay from $pp$ collisions at $\sqrt{s} = 8$ TeV}}. Phys. Lett. B {\bf{753}} 424, 2016.
\bibitem{Belle} Belle Collaboration, {\it{Angular analysis of $B^0 \to K^{*0}(892) \to l^+ l^-$}}, arXiv:[hep-ex] 1604.04042
\bibitem{ABSZ} W. Altmannshofer and D.M. Straub, {\it{New physics in $b \to s$ transitions after LHC run 1}}, Eur. Phys. J. C {\bf{75}} (2015) 382 [arXiv:1411.3161].
\bibitem{DHMV} S. Descotes-Genon, L. Hofer, J. Matias and J. Virto, {\it{On the impact of power corrections in the prediction of $B_d \to K^* \mu^+ \mu^-$ observables}}, JHEP {\bf{12}} (2014) 125 arXiv:1407.8526.

\end{thebibliography}


\end{document}
